\clearpage
\addsec{List of Symbols}
\chaptermark{List of Symbols}

\small

\newsavebox\ltmcbox

\begin{multicols}{2}
\medskip

\setbox\ltmcbox\vbox{
\makeatletter\col@number\@ne
\begin{longtable}{l l}

$A^\pm$				&					Forward/backward amplitude \\
$\mathrm{a}$		&					Absorption\\

$\B$				&					Magnetic field \\

$\Cn$				&					Complex contour\\
$\c$				&					Vacuum speed of light \\

$\D$				&					Electric displacement field \\
$\Dpl$				&					Plasmon density of states \\

$\E$				&					Electric field \\
$\mathrm{e}$		&					Electron \\
$\mathrm{e}$		&					Emission\\
$\ex$				&					Unit vector in $x$ direction \\

$\f$			&					Fermi function \\

$G$				&					Polarisability aux. function \\
$\Gp$			&					Pol. derivative aux. function \\
$\Gpl$			&					Recombination rate density \\

$\H$				&					Magnetic H field \\
$\mathrm{h}$		&					Hole \\
$\ħ$				&					Dirac's constant \\

$\J$				&					Current density \\
$\Js$				&					Surface current density \\

$\k$				&					Fermion wavevector \\
$\kB$				&					Boltzmann's constant \\

$\M$				&					Magnetisation field \\
$\Mtr$				&					Transfer matrix\\
$m$					&					Carrier inversion parameter \\
$\mc$				&					Critical branching parameter \\

$N$					&					Emitter density \\
$\Ne$				&					Fermion number density \\
$\Ndot$				&					Fermion net generation rate \\
$\NdotPump$			&					Number density pump rate \\
$\NdotRel$			&					Number density relaxation rate \\
$\npar$				&					Refractive index \\
$\nβ$				&					Boson number \\
$\nβdot$			&					Boson net generation rate \\
$\nβdotrel$			&					Boson relaxation rate \\
$\nβeq$				&					Boson number \\

$\P$				&					Polarisation field \\
$\mathrm{pl}$		&					Plasmon \\
$\mathrm{ph}$		&					Phonon \\

$\Q$				&					\threed boson wavevector\\
$\q$				&					\twod boson wavevector \\
$\qc$				&					High wavevector cutoff \\

$\Rspon$			&					Plasmon emission rate \\
$\Rβ$				&					Carrier relaxation rate \\
$\rp$				&					Electrical pump rate \\
$\rβλ(\q)$			&					Boson spectral emission rate \\

$\S$				&					Poynting vector \\
$\Sβλ$				&					Energy relaxation rate \\

$\T$				&					Temperature \\
$\Tamb$				&					Ambient temperature \\
$\Tc$				&					Carrier temperature \\
$\t$				&					Time \\

$\Ue$				&					Fermion energy density \\
$\Udot$				&					Energy density net rate \\
$\UdotPump$			&					Energy density pump rate \\
$\UdotRel$			&					Energy density relaxation rate \\
$\ud$				&					Dispersion loss \\
$\ug$				&					Group loss \\
$\uTE$				&					Transfer matrix layer parameter \\

$\vb$				&					Band velocity \\
$\vd$				&					Dispersion velocity \\
$\vF$				&					Fermi velocity \\
$\vg$				&					Group velocity \\
$\vp$				&					Phase velocity \\

$\x$				&					Position vector \\

$\Zf$				&					Vacuum impedance \\
$\Zpar$				&					Wave impedance \\

$\αf$				&					Vacuum fine structure constant \\
$\αg$				&					Graphene fine structure const.\\

$\γabs$				&					Plasmon absorption rate \\
$\γL$				&					Drude-Lorentz width \\
$\γemit$			&					Plasmon stim. emit. rate \\
$\γp$				&					Drude loss \\
$\γpl$				&					Plasmon frequency imag. part \\
$\γplabs$			&					Plasmon absorption rate \\
$\γplemit$			&					Plasmon stim emission rate \\
$\γpump$			&					Pump width \\
$\Γple$				&					Fermion recombination rate \\

$\ΔN$				&					Inversion density \\
$\Δq$				&					Stopped light spatial bandwidth \\
$\Δt$				&					\textsc{Fdtd} timestep \\
$\Δx$				&					\textsc{Fdtd} cell size \\
$\Δω$				&					\textsc{Sl} frequency bandwidth \\

$\εpar$				&					Permittivity \\
$\εbar$				&					Average permittivity\\
$\εbg$				&					Background permittivity\\
$\εf$				&					Vacuum permittivity \\
$\εinf$				&					High frequency permittivity \\
$\εL$				&					Drude-Lorentz permittivity \\
$\εRPA(\q,\ω)$		&					\textsc{Rpa} dielectric function \\
$\εtens$			&					Permittivity tensor \\
$\έ$				&					Fermion energy \\
$\έtilM$			&					Fermion matsubara frequency \\

$\μpar$				&					Permeability \\
$\μ$				&					Chemical potential \\
$\μbar$				&					Scale energy \\
$\μe$,$\μh$			&					Electron fermi level \\
$\μf$				&					Vacuum permeability \\
$\μtens$			&					Permittivity tensor \\

$\Π$				&					Polarisability \\
$\Πe$				&					Electron partial polarisability \\

$\ρ$				&					Charge density \\
$\ρs$				&					Sheet charge density \\

$\Σabs$				&					Plasmon absorption polarisability \\
$\Σemit$			&					Plasmon stim. emit. polarisability \\
$\σe$				&					Emission cross-section \\
$\σs$				&					Sheet conductivity \\
$\σsinter$			&					Interband sheet conductivity \\

$\τpl$				&					Plasmon lifetime \\

$\χe$				&					Electric susceptability \\
$\χL$				&					Drude-Lorentz susceptability\\
$\χm$				&					Magnetic susceptability \\

$\ω$				&					Boson frequency \\
$\ωL$				&					Drude-Lorentz freqeuncy\\
$\ωp$				&					Drude-Lorentz plasma frequency \\
$\ωpl$				&					Plasmon frequency solution \\
$\ωpump$			&					Pump frequency \\
$\ωsp$				&					Surface plasmon frequency \\

\end{longtable}
\unskip
\unpenalty
\unpenalty}

\unvbox\ltmcbox

\medskip
\end{multicols}

\normalsize

Many quantities in this list can apply to multiple species, i.e. $\nβ$ is the
number of bosons.
Similar quantities, $\npl$, $n_\mathrm{ph}$ apply more specifically to plasmons
and phonons.
For brevity these have been omitted.
The same applies to fermions, electrons, and holes, etc.
Also for brevity, variants of variables such as Fourier transforms, vector
norms, and scaled versions of quantities (discussed in \sec{scale}),
are omitted.

